---
title: "Gc_chisquare"
author: "Andrea Cheung"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Collaborated check

It's Andrea again, and i'm updating some text. 


Hi it's Angie. I'm the collaborator
hi again


Getting data loaded, loading tidyverse, and getting some summary coats
```{r}
library(tidyverse)
gc_df <- read_csv("gc_df.csv")

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns !="NA") %>% 
  count(gender, make_get_guns) %>% #makes groupings based on catagorical variables
  spread(make_get_guns, n) %>%  # makes it look like a contingency table 
  select(-gender)

rownames(get_guns) <- c("Female", "Male") 
View(get_guns)

```

I'm the collaborator and I'm going to do chi square.

Is there a significant association between gender and opinion on access to guns?

Chi Square

```{r}
guns_prop <-prop.table(as.matrix(get_guns), 1) #make table of proportions for each group first
guns_prop

#Perform chi-square

guns_x2 <- chisq.test(get_guns) #run x2 test
guns_x2


```

Recommended govern action on gun access differs significantly between males and females ($\chi^2$(`r guns_x2$parameter`)). Maybe include table in document, and point out biggest difference in text.

Chi square doesn't have an effect size. But you cna list actual differences.
